Symmetric Peer-to-Peer Applications

### 2022-09-10 tpd-22.tex
...

\begin{figure*}[t]
  \centering
  \includegraphics[width=\linewidth]{topo}
  \caption{
    \label{fig.topo}
    TODO
  }
\end{figure*}

We simulate the application with $21$ peers using the mixed topology of
Figure~\ref{fig.topo}, with peers organized in straight lines, long cycles, and
short cycles.
%
In order to have an absolute clock to compare peers, we use a single machine
to simulate all peers, and merge their logs into a single file constituting a
shared timeline.
%
We simulate the network latency and clock drift in software with random delays.

We now detail how we instrument the middleware implementation measure the
properties above:
%
\begin{enumerate}
%
\item \textbf{Recurrence of time travels:}
Every time a peer is ahead of time and needs to travel back, we output its id
and how much ticks it needs to travel back.
At the end, we measure the percentage of the sum of all time travel ticks over
the total simulation ticks.
As an example, if all peers sum $1000$ time travel ticks over $100k$
accumulated simulation ticks, then the final measure is $1\%$.
%
\item \textbf{Real-time pace of peers:}
We start each peer with a random delay of up to $10s$ to force a time mismatch.
We also force exaggerated clock drifts in random peers ($1ms$ every $1h$).
and then verify if they synchronize and remain synchronized during the whole
simulation.
We teak the middleware to output its current tick every $100ms$.

@@

%
\end{enumerate}

>>>>

\begin{figure*}[t]
  \centering
  \includegraphics[width=\linewidth]{topo}
  \caption{
    \label{fig.topo}
    Network topology: 21 peers organized as a straight line ($0--3$), a simple
    cycle ($3--8$), a second straight line ($8--11$), a full connected cycle
    ($12--17$), and a third straight line ($17--20$).
    An optional link ($0,20$) creates a long cycle in the network.
  }
\end{figure*}

We simulate the application with $21$ peers using the mixed topology of
Figure~\ref{fig.topo}, with peers organized in straight lines and cycles.
%
In order to have an absolute clock, we use a single machine to simulate all
peers, allowing us to merge their logs into a single file with a comparable
shared timeline.
%
We simulate the network latency in software with random delays.

Figure~\ref{TODO} results...

We now detail how we instrument the middleware implementation measure the
properties above:
%
\begin{enumerate}
%
\item \textbf{Recurrence of time travels:}
Every time a peer is ahead of time and needs to travel back, we output its id
and how much ticks it needs to travel back.
At the end, we measure the percentage of the sum of all time travel ticks over
the total simulation ticks.
As an example, if all peers sum $1000$ time travel ticks over $100k$
accumulated simulation ticks, then the final measure is $1\%$.
%
\item \textbf{Real-time pace of peers:}
We start each peer with a random delay of up to $10s$ to force a time mismatch.
Each peer outputs its current tick continuously, allowing us to compare them
in the shared timeline.
Each time we see a greater tick, we count how many smaller ticks from other
peers appear in the timeline, which means that they are ...
\item \textbf{Correctness of unstable peers:}
- state (even for stable peers)
- time
%
\end{enumerate}

After $Xs$, .
and then verify if they synchronize and remain synchronized during the whole
simulation.
We teak the middleware to output its current tick every $100ms$.

@@
